Verifying Demonstrations

### 2018-05-29 paper/analysis-security.tex
Adds draft of mechanism reuse prevention

>>>>

There is also another case of collision that we must prevent.
Consider that Alice computes \(\pid = \ACprf[_\sk][\cid]\) for some cause 
identifier \(\cid\) and some witnesses computes \(\wid_1, \dotsc, \wid_n\), 
with \(\wid_i = \ACprf[_{\sk_i}][\pid]\).
Now, if Alice would construct a manifesto \(m\) such that \(\Hash[m] = \pid\), 
then \(\wid_1, \dotsc, \wid_n\) would be valid participant identifiers for the 
protest with manifesto \(m\).
This means that we must separate the mechanisms used for participating and 
witnessing.
The protocol achieves this by the fact that \[
  \prf_{\wid} = \SPK[\sk_i][\dotsc][\pid, \wid, t_s, t_s', l]
\]
does not include \(\cid\) whereas \[
  \prf_{\pid} = \SPK[\sk_i][\dotsc][\cid, \pid, \wid, t_s, t_s', l]
\]
does.
Thus the verification process differs for the two types of proofs.
(An alternative approach would have been to compute them differently, \eg 
\(\pid = \AC[PRF]_{\sk}(x)\) but \(\wid = \AC[\overline{PRF}]_{\sk}(x)\).
